% Michael Sipes Resume
% 2025-08-29
% mjsipes@gmail.com
% 10 Horseshoe Ct, Hillsborough, CA, 94010
% 650-766-4063
% (650) 766-4063
% https://github.com/mjsipes
% https://www.linkedin.com/in/mjsipes

% pdflatex michael_sipes_resume.tex

\documentclass[a4paper,10pt]{article}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{left=0.6in, right=0.5in, top=0.5in, bottom=0.5in}
\pagestyle{empty}

\begin{document}

% Name and Contact Information
\noindent
\begin{center}
    \textbf{\huge Michael Sipes} \\
    \vspace{5pt}
    \href{https://github.com/mjsipes}{GitHub} $|$ 
    \href{https://www.linkedin.com/in/mjthefox}{LinkedIn} $|$ 
    \href{mailto:mjsipes@gmail.com}{mjsipes@gmail.com} $|$ 
    (650) 766-4063
\end{center}

% Education
\section*{Education}
\noindent
\textbf{University of Southern California} \\
\textit{M.S. in Computer Science} \hfill 2025 - 2026 \\
\textit{B.S. in Computer Science} \hfill 2021 - 2025


% \noindent \textbf{GPA:} 3.54 \\
\noindent \textbf{Relevant Coursework:} Artificial Intelligence, Machine Learning, Operating Systems, Internetworking, Database Systems, Web Technologies, Software Engineering, Computer Systems, Analysis of Algorithms, Data Structures \\
\noindent \textbf{Languages:} C++, C, Python, Java, JavaScript, TypeScript, HTML, CSS, SQL, Bash, Markdown, LaTeX, Assembly \\
\noindent \textbf{Frameworks / Technologies:} React, Next.js, OpenAI API, Vercel AI SDK, Supabase, Zustand, Tailwind CSS, shadcn/ui, PyTorch, RESTful APIs, Docker, Git, Vercel, Vite, npm, HTTPie 
% Experience
\section*{Experience}

\noindent
\textbf{RingCentral} \\
\textit{AI Software Engineering Intern} \hfill June 2024 - August 2024
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item Built a retrieval-augmented generation system to detect and consolidate duplicate content across a knowledge base of 2,000+ articles.
    \item Conducted interviews with article writers, understood their workflow challenges, and defined technical requirements for the solution.
    \item Implemented the solution by generating semantic embeddings with OpenAI and storing them in Supabase (pgvector extension) to enable similarity search.
\end{itemize}

% Academic Projects
\section*{Academic Projects}

\noindent
\textbf{DrawTunes} \hfill \href{https://drawtunes.vercel.app/}{Live Demo} $|$ \href{https://github.com/mjsipes/drawtunes}{GitHub}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item Built AI-powered music discovery platform where users draw artwork to receive personalized song recommendations using React, TypeScript, and Supabase edge functions.
    \item Refactored state management migration from React Context to Zustand, reducing unnecessary re-renders and optimizing performance across interconnected components.
    \item Implemented modular serverless architecture processing image uploads through OpenAI Vision API and iTunes API integration for real-time music recommendation delivery.
\end{itemize}

\vspace{10pt}
\noindent
\textbf{Layers} \hfill \href{https://layers4.vercel.app/}{Live Demo} $|$ \href{https://github.com/mjsipes/layers4}{GitHub}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item Built AI-powered skiing outfit recommendation app that learns from user feedback to provide personalized clothing recommendations based on personal comfort data and weather conditions.
    \item Implemented dual interface architecture where both traditional UI and AI chat perform identical database operations, ensuring feature parity and consistent user experience across interaction modes.
    \item Integrated real-time weather data and location services to automatically adjust recommendations based on current conditions at user's ski resort.
\end{itemize}

\vspace{10pt}

\noindent
\textbf{Mjsipes Photography} \hfill \href{https://mjthefox.com/}{Live Demo} $|$ \href{https://github.com/mjsipes/mjthefox}{GitHub}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item Built personal photography portfolio using Next.js and Supabase Storage to match Squarespace display quality while adding AI-generated artistic reinterpretations of 300 personal photographs.
    \item Implemented dynamic page routing and metadata database architecture designed for experimental workflows, tracking relationships between original photos and AI style variations.
    \item Implemented automated image processing pipeline using Node.js scripts and OpenAI Images API to generate 1,800 style-transfer variations across 6 artistic styles.
\end{itemize}

\vspace{10pt}

\noindent
\textbf{Tennis Probability Model} \hfill \href{https://tennis-sipes.vercel.app/}{Live Demo} $|$ \href{https://github.com/mjsipes/tennis}{GitHub}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item Built tennis match simulator using recursive probability algorithms in Python to analyze win probabilities across different match formats and player skill levels.
    \item Implemented dynamic probability calculations tracking game state transitions, serving advantages, and point importance scoring throughout match progression.
    \item Implemented statistical analysis framework demonstrating that point importance varies dramatically based on match context, with late-game points having exponentially higher impact on match outcomes.
\end{itemize}

% \noindent
% \textbf{Lingo LLM} \hfill \href{https://lingo-llm.vercel.app/}{Live Demo} $|$ \href{https://github.com/mjsipes/lingo-llm}{GitHub}
% \begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
%     \item Built multi-agent AI language learning platform using React, TypeScript, and Supabase orchestrating Claude, OpenAI, and Groq APIs through specialized anthropomorphic characters for children's Spanish education.
%     \item Implemented intelligent context management system with smart conversation summarization and selective message persistence to maintain character awareness without overwhelming AI models.
%     \item Implemented modular agent architecture where specialized characters handle distinct capabilities (translation, image generation, storytelling) while maintaining seamless user experience through coordinated AI responses.
% \end{itemize}

% \vspace{10pt}

% \noindent
% \textbf{F1Racer Sipes} \hfill \href{https://www.f1racersipes.com/}{Live Demo} $|$ \href{https://github.com/mjsipes/f1racersipes-react}{GitHub}
% \begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
%     \item Built multiplayer racing game using React and Supabase for live competition between players.
%     \item Implemented real-time synchronization using Supabase Realtime channels for instant game state updates across all connected players.
%     \item Implemented secure user authentication and PostgreSQL database integration, deployed to Vercel for production hosting.
% \end{itemize}

% \vspace{10pt}

% \noindent
% \textbf{Stock Algorithms: An Exploration} \hfill \href{https://stock-algorithms.vercel.app/}{Live Demo} $|$ \href{https://github.com/mjsipes/stock_algorithms}{GitHub}
% \begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
%     \item Built quantitative trading analysis system using Python comparing perfect foresight vs. greedy algorithms across stocks and cryptocurrencies.
%     \item Implemented minute-by-minute trading simulation achieving 10.75\% daily returns on Apple and 35.44\% on Dogecoin, demonstrating volatility impact on performance.
%     \item Implemented comprehensive fee analysis revealing that high-frequency trading costs (600 trades/day at 0.1\% fees) eliminate profits in real-world scenarios.
% \end{itemize}

% \vspace{10pt}

% \noindent
% \textbf{PyTorch Deep Learning Notebooks} \hfill \href{https://github.com/mjsipes/pytorch_notebooks}{GitHub}
% \begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
%     \item Built PyTorch experimentation notebooks exploring neural network fundamentals through custom implementations of linear regression, matrix regression, and polynomial feature engineering models.
%     \item Implemented controlled experiments investigating gradient behavior with random noise injection and parameter initialization strategies, analyzing training dynamics across different model architectures.
%     \item Implemented mathematical exploration into non-linear function approximation using ReLU activation functions, studying the relationship between model complexity and function fitting accuracy.
% \end{itemize}

% Honors
\section*{Honors}
\noindent
Sydney Harmon Academy for Polymathic Study Fellow 2025, Effective Altruism Fellow 2022

\end{document}
